Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
finished preliminary examples section

In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin-canonical divisors.

@@

\begin{example}
\label{eg:base-1-0}
Let $(\sx',0,\halfcan')$ be a log stacky curve of genus $g = 1$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

@@

\begin{example}
\label{eg:exception-1-5}
Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P - Q + \frac{2}{5}P_1.$ Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that
$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$

>>>>

In this subsection, we present a definition of admissibility, which is quite similar to that defined in Voight and Zureick-Brown \cite[Definition 8.5.1]{vzb:stacky}, but is adapted to the case of spin canonical divisors.

@@

In this section, we compute several examples of computing presentations for spin canonical rings. In several cases, we also check certain triples are admissible, as defined in Definition ~\ref{defn:admissible}. In addition to demonstrating the algorithmic procedure for computing presetations, these examples will also serve as useful base cases for our inductive proof of Theorem ~\ref{thm:main}.

\begin{example}
\label{eg:base-1-0}
Let $(\sx',0,L')$ be a log stacky curve of genus $g = 1,$ with $\halfcan' = 0$. In the case $\halfcan' = 0,$ it is immediately clear that $R_{\halfcan'} \cong k[x]$ with $x$ a generator in degree 1.
\end{example}

@@

\begin{example}
\label{eg:exception-1-5}
Let $(\sx', 0, L')$ be a log spin curve of genus 1 so that $L' = P - Q + \frac{2}{5}P_1.$ Let $u \in (P_L)_1$ be any nonzero element. We obtain $\di u|_{P_1} = 0,$ since $2P -2Q \sim 0$ and by Riemann--Roch, $\dim_k (P_L)_1 = 1.$ Let $y_3 \in (R_L)_3$ be any nonzero element. We obtain $\di y_3|_{P_1} = - P_1,$ by Riemann Roch, since if $y_3$ did not have a pole at $R$, we would obtain $y_3 \in H^0(\sx,3P-3Q) \cong H^0(\sx, P - Q) \cong 0$ as $P \neq Q$. Finally, let $y_5 \in (R_L)_5$ be an element with $y_5|_{P_1} = -P_1$. Then, we claim there is some $\alpha \in k$ so that

$$R_L \cong k[u, y_3, y_5]/(y_3^4 - \alpha uy_5^2).$$
